Stability in human interaction networks: primitive typology of vertex, prominence of measures and time activity statistics

### 2015-04-27 paper.tex
added initial supporting information file
first version with all figures

For the histograms used in the classification process, the use of at least $\eta$ vertices for each bin did not yield significant differences.
That was understood as a consequence of the observation scale (see Appendix~\ref{ap:ded}).

@@

\subsection{Effect of scale in histogram smoothing}\label{ap:ded}
There are between 20 and 200 participants in the message window sizes used to derive most of the results ($ws \in [200,1500]$ messages). As peripheral vertices are abundant and span few degrees, there are more than $\eta$ vertices with each low degree value. For the case of higher degrees, one should consider that with the $ws$ used, each participant is $p \in [0.1\%,0.5\%]$ of all participants. Therefore, if incident connectivity is very improbable in an Erd\"os R\'enyi network (less than $p$, the probability that a single participant represents when the histogram is normalized to the density function), than it is not an intermediary connectivity, but a hub. Therefore, using at least $\eta$ vertices for each bin did not impact the results.

@@

%
%\begin{figure*}
%    \centering
%        \includegraphics[width=\textwidth]{pcm}
%        \caption{Pulse Code Modulation (PCM) audio: an analogical signal is represented by 25 samples with 4 bits each.}
%        \label{fig:PCM}
%\end{figure*}
%

>>>>

For the histograms used in the classification process, the use of at least $\eta$ vertices for each bin did not yield significant differences.
That was understood as a consequence of the observation scale (see Appendix~\ref{ap:ded2}).

@@

\subsection{Effect of scale in histogram smoothing}\label{ap:ded2}
There are between 20 and 200 participants in the message window sizes used to derive most of the results ($ws \in [200,1500]$ messages). As peripheral vertices are abundant and span few degrees, there are more than $\eta$ vertices with each low degree value. For the case of higher degrees, one should consider that with the $ws$ used, each participant is $p \in [0.1\%,0.5\%]$ of all participants. Therefore, if incident connectivity is very improbable in an Erd\"os R\'enyi network (less than $p$, the probability that a single participant represents when the histogram is normalized to the density function), than it is not an intermediary connectivity, but a hub. Therefore, using at least $\eta$ vertices for each bin did not impact the results.

@@
